---
title: "Scientifique Reporting "
author: "Groupe 144"
date: "14.05.21"
output:
  pdf_document:
    toc: true
#theme: united
    
---

Hi, how are you?

good thanks <3 

omg yess

```{r setup, include=FALSE}


knitr::opts_chunk$set(echo = TRUE)
```




```{css, include= FALSE}

h1{color:blue}
h2{color:green}
knitr::opts_chunk$set(echo = TRUE)
```


*requirements for the written report*
*in pdf, max 4 pages, font:11pt*

# **Groupe Project (title) *(be imaginative but precise)* **

Participants: "Camille Blaise, Joana Schaller, Noémie Sandjo, Livia Courteaud, Luisa Lendi"
*The name of the participants in the group*


## Description of the task 
*A description of the task that was assigned to the group*



## Motivation and utility of the task 

*A motivation of what such a task can bring as additional knowledge, possibly compared to other
approaches*

## Task, and Code 

```{r
*code insert here* 
}
```

## Description and interpretation of the obtained results 
*A description and interpretation of the obtained results*


## Evaluation of results
*An explanation on why the obtained results were expected or not*

## statistical methods
*An explanation on the statistical methods that were used and if they can be used in other contexts
that the ones of the term project*

## acquired skills 

*A description of the skills acquired during the execution of the term project*

*at least one additional element, that will be evaluated
for its originality and relevance*



```{r cars}
summary(cars)
```



```{r pressure, echo=FALSE}
plot(pressure)
```
